---
title: "SentinelReadr"
author: "Pieta Schofield"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{SentinelReadr}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup,results="hide"}
library(tidyverse)
library(sentinelreadr)
```

# Introduction

This is a small package that simplifies the extraction of the data that is stored in xml inside RSNTL file. At the present there are three main function

- read_rsntl() which extract the xml elements from the RSNTL file and creates a list of xml documents
- testdetails_xml_to_table() coverts the testdetails section of the file into a data.table
- clinical_xml_to_table() that converts the clinical data elements into data.tables

```{r read_file}
input_filename <- system.file("extdata","2013_B_07-01-2021_13-49-43.RSNTL",package="sentinelreadr")
xml <- read_rsntl(input_filename,chkDMV=T)
```

The test data section can be decoded to a tibble. Because the xml object returned buy the read_rstnl() 
funtion is a list of lists it is best to use the lapply function to the various items in the xml object

```{r xml-object}
is(xml)
summary(xml)
lapply(xml,is)
```

```{r get-testdetails}
patient <- lapply(xml$test_details,testdetails_xml_to_table)
DT::datatable(patient[[1]])
```

The summary shows that there are two datasets in this file

```{r display-tables1}
data <- lapply(xml$clinical_data,clinical_xml_to_table)
DT::datatable(data[[1]])
```

However it appears they are the same data

```{r display-table2}
DT::datatable(data[[2]])
```

This data is plotable

```{r plot,fig.with=12}
library(ggplot2)
gg <- ggplot(data[[2]],aes(x=Time,y=Systolic)) + geom_point(colour="blue") 
plot(gg)
```

Reading the other files

```{r test-other-files}
input_filename <- system.file("extdata","2014_B_07-01-2021_13-49-44.RSNTL",package="sentinelreadr")
xml <- read_rsntl(input_filename,chkDMV=T)
```

Get test details

```{r test-details-2}
patient <- lapply(xml$test_details,testdetails_xml_to_table)
DT::datatable(patient[[1]])
```

Get data details

```{r data-details-2}
data <- lapply(xml$clinical_data,clinical_xml_to_table)
DT::datatable(data[[1]])
```

Read file 3

```{r read-file-3}
input_filename <- system.file("extdata","2011_B_07-01-2021_13-49-41.RSNTL",package="sentinelreadr")
xml <- read_rsntl(input_filename,chkDMV=T)
```

Get test details file 3

```{r test-details-3}
patient <- lapply(xml$test_details,testdetails_xml_to_table)
DT::datatable(patient[[1]])
```

Get data details 3

```{r data-details-3}
data <- lapply(xml$clinical_data,clinical_xml_to_table)
DT::datatable(data[[1]])
```

## Errors


```{r test-other-files}
input_filename <- system.file("extdata","2014_B_07-01-2021_error_1.RSNTL",package="sentinelreadr")
xml <- read_rsntl(input_filename,chkDMV=T)
```


```{r test-other-files}
input_filename <- system.file("extdata","2014_B_07-01-2021_error_2.RSNTL",package="sentinelreadr")
xml <- read_rsntl(input_filename,chkDMV=F)
```

