---
title: "SentinelReadr"
author: "Pieta Schofield"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{SentinelReadr}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup,results="hide"}
library(sentinelreadr)
```

# Introduction

This is a small package that simplifies the extraction of the data that is stored in xml inside RSNTL file. At the present there are two main function

- read_rsntl() which extract the xml elements from the RSNTL file and creates a list of xml documents
- clinical_xml_to_table() that converts the clinical data elements into data.tables

```{r read_file}
input_filename <- system.file("extdata","2013_B_07-01-2021_13-49-43.RSNTL",package="sentinelreadr")
input_filename
xml <- read_rsntl(input_filename)
data <- lapply(xml$clinical_data,clinical_xml_to_table)
summary(data)
```

The summary shows that there are two datasets in this file

```{r display-tables1}
DT::datatable(data[[1]])
```

However it appears they are the same data

```{r display-table2}
DT::datatable(data[[2]])
```

This data is plotable

```{r plot,fig.with=12}
library(ggplot2)
gg <- ggplot(data[[2]],aes(x=Time,y=Systolic)) + geom_point(colour="blue") 
plot(gg)
```
